Toy Transit Surveys

### 2017-08-30 memos/workdir/toy_analytic_surveys.tex
memo: update abstract

Then, we allow the properties of the secondary in binary systems to vary. A 
distribution of light ratios introduces a heavy detection bias towards 
equal-mass binaries in magnitude limited samples.
We show that dependent upon planet occurrence's functional dependence on host 
star mass (and binarity), the errors introduced in derived occurrence rates vs. 
real occurrence rates can range from a few percent to at most $\approx 60\%$ 
relative error.

>>>>

We then allow the properties of the secondary in binary systems to vary. A 
distribution of light ratios introduces a detection bias towards 
equal-mass binaries in magnitude limited samples.
We show that dependent upon planet occurrence's functional dependence on host 
star mass, as well as the specifics of the assumed survey completeness, the 
occurrence rate correction factor $X_\Gamma \equiv \Gamma_{\rm 
true}/\Gamma_{\rm obs}$ ranges from $0.6-1.6$.
